Lateral Inhibition Nets with Nonlinear Connections

### 2017-05-01 paper.tex
paperdone

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Data-driven Sparse Connections for \\Deep Convolutional Neural Network}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Convolutional Neural Networks(CNNs) have achieved great success in
many computer vision tasks, especially in image recognition. However,
as neural networks grow deeper and deeper, to some extend, we've found
them becoming difficult to train, and requiring samples in large scale
dramatically, even with the help of Dropout and Drop-connect methods,
which do improve the accuracy a bit but burdens the training process as
a sacrifice. To overcome this, we proposed a novel method to generate
dynamic graphs of computation for varied inputs. As our computation
graphs are determined by input samples and proved to be pretty sparse,
we call them Data-driven Sparse Connections(DSCs). We've applied our DSCs
to a few popular image recognition tasks, and it is shown deep CNNs with
DSCs win over the state-of-the-art on many tasks, such as MNIST, FICAR-10,
and FICAR-100, to name a few.
\end{abstract}

@@

\section{Nonlinear Connections with Bounded Parameters}
Inspired by biological neuron synapses\cite{hall1905textbook,
bayliss1908reciprocal,gerard1941interaction}, we propose a new computation
model for connections between neurons. In connection models known so far,
the most popular and probably the most useful one \cite{jain1996artificial} is :
$$ y=\sigma\left(\sum_{i=1}^{N}w_ix_i+b\right) $$
While, the activation function $\sigma(\cdot)$ can be the sigmoid function
$sigmoid(x)=\frac{1}{1+e^{-x}}$, or $tanh(x)$,
or ReLU function $ReLU(x)=max(0,x)$\cite{nair2010rectified}.
In addition,
a different form of activation function, $maxout(x)=max_{i=1}^N(w_ix_i)$,
is being used in CNNs recently\cite{goodfellow2013maxout}.
However, these activation functions are all neuron-based, and simply suppose
that each connection acts as simple as a linear function, $o(x_i)=w_ix_i$,
in which, $w_i$ is a float number without even a bound. While in biological
neural system, synapses, mimicked by artificial connections, are not really
behaving linearly. In synapses, signals are transformed from electrical form
to chemical one, and transferred by some proteins to a connected neuron,
then again, transformed back to electrical form to inhibit or activate
the connected neuron\cite{gray1959axo,harvey2007locally}. In this process,
signals can be amplified or reduced, but not in a linear way. Futhermore,
signal strengths have lower and upper bounds which differs from the denotation
of connections in CNNs. Thus we propose a new model for artificial neurons and
their connections. Suppose, there're 3 neurons, $\mathcal{N}_a$,$\mathcal{N}_b$,
$\mathcal{N}_c$, and 2 connections, $\mathcal{C}_{a\rightarrow c}$,
$\mathcal{C}_{b\rightarrow c}$, the graph is shown in figure
(\ref{fig:neurons}).

\begin{figure}
\centering
\includegraphics[height=24mm]{paper_res/conn.png}
\caption{Neurons and Connections}
\label{fig:neurons}
\end{figure}

As synapses have two kinds: excitatory and inhibitory ones
\cite{uchizono1965characteristics,wilson1972excitatory},
we propose two categories of connections the same way.
For excitatory connections, as $\mathcal{C}_{a\rightarrow c}$
shown in figure (\ref{fig:neurons}), their signal
transferring functions are described as equation
(\ref{eq:excitatory-transfer}), in which, $\alpha\in(0,1)$
is guaranteed.
For excitatory connections,
\begin{equation}
    g^{+}(x)=min\left(max\left(0,\frac{x-\alpha}{1-\alpha}\right),1\right)
    \label{eq:excitatory-transfer}
\end{equation}

@@

For a $M$-layer neural network, The forward-computaton equation for the
$k$th neuron on $(p+1)\text{th}(p=1,2,\cdots,M)$ layer,
$\mathcal{N}_{p_k}$, with the input layer denoted as the first layer, is

@@

In which, $g_{i\rightarrow{k}}$ is the signal transferring function from
$i$th neuron in $p$th layer to $k$th neuron
in $(p+1)$th layer,
and $o_{p_i}$ is the activation value of the $i$th neuron on
$p$th layer.

@@

While, since the equations for connections and activation function
of neurons in our model are not really differentiable, the famous
backprop algorithm cannot be applied in the training section. Thus,
we propose a training algorithm that deals with non-differentiable
situation like this.

Firstly, let's introduce two model parameters: $\xi$ and $\eta$,
they together determine the learning rate of our model. In addition,
$\xi\in(0,1)$ and $\eta\in(0,1)$. Let
$x=\sum_{i=1}^{N_p}g_{i\rightarrow{k}}(o_{p_i})$, $y=\sigma(x)$, and the given
feedback error for current neuron $\mathcal{N}_{p_k}$ is $\Delta y$.
Similarly, the feedback error for $x$ is $\Delta x$. In case parameter $\alpha$
goes to 1 and fails our equations, we propose a upper-bound $\alpha_{max}$, which
is very close to 1 but less than 1.
Thus, the parameter updatng rules are,

@@

\begin{equation}
\Delta{\alpha} =\xi\cdot\left\{
    \begin{aligned}
        &\left(max\left(0,\hat{\alpha}\right)-\alpha\right),&\Delta{y}>0\\
        &\left(min\left(\alpha_{max}, \hat{\alpha}\right)-\alpha\right),&\Delta{y}<0\\
    \end{aligned}
    \right.
\label{eq:delta-alpha}
\end{equation}

@@

Let $\alpha_{p_{i\rightarrow{k}}}$ be the parameter of the connection from the
$i$th neuron in $p$th layer to the $k$th neuron in ($p+1$)th layer.
Using equation (\ref{eq:delta-alpha}), we can update the parameters of connections.
For excitatory connections,

@@

\begin{equation}
    \Delta\alpha_{p_{i\rightarrow{k}}} =\xi\cdot
    \left\{
        \begin{aligned}
            &max\left(0,\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}>0\\
            &min\left(\alpha_{max},\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}<0\\
        \end{aligned}
        \right.
    \label{eq:conn-update-pos}
\end{equation}

@@

\begin{equation}
    \Delta\alpha_{p_{i\rightarrow{k}}} =\xi\cdot
    \left\{
        \begin{aligned}
            &min\left(\alpha_{max},\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}>0\\
            &max\left(0,\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}<0\\
        \end{aligned}
        \right.
    \label{eq:conn-update-neg}
\end{equation}

@@

We propose a valve $\tau\in(0,\alpha_{max})$, which is very close to 0 but greater
than 0, if $g_{p_{i\rightarrow{k}}}=g^{+}$, $\Delta x_{p+1_{i\rightarrow{k}}}<0$
and $\alpha_{p_{i\rightarrow{k}}}+\Delta\alpha_{p_{i\rightarrow{k}}}-\alpha_{max}<\tau$,
then for connection $\mathcal{C}_{p_{i\rightarrow{k}}}$, let $g_{p_{i\rightarrow{k}}}=g^{-}$, this update will
switch connections from excitatory to inhibitory.
Similarly, if $g_{p_{i\rightarrow{k}}}=g^{-}$, $\Delta x_{p+1_{i\rightarrow{k}}}>0$
and $\alpha_{p_{i\rightarrow{k}}}+\Delta\alpha_{p_{i\rightarrow{k}}}-\alpha_{max}<\tau$,
then for connection $\mathcal{C}_{p_{i\rightarrow{k}}}$, let $g_{p_{i\rightarrow{k}}}=g^{+}$, this update will
switch connections from inhibitory to excitatory.

So far we've derivated the equations for updating parameters of neurons
in $(p+1)$th layer and the parameters of connections from $p$th layer to
$(p+1)$th layer. With equation (\ref{eq:delta-x-real}),(\ref{eq:conn-error})
and (\ref{eq:delta-x}), we calculate the error of the output in the $p$th layer,
Let $\Delta o_{p_{i\rightarrow{k}}}$ be the correction for $\mathcal{N}_{p_i}$
contributed by connection $\mathcal{C}_{p_{i\rightarrow{k}}}$,
for excitatory connections,

@@

\section{Competition Between Filters: Filter Alienation within Same Layer}
For filters in the same layer, to reduce replication and extract features
from an image as many as possible, filter alienation is essential. Thus we
propose a pretraining algorithm for filter initialization.
Let $\mathcal{F}_{p_k}$ denote the $k$th filter in layer of
depth $p$, and $o_{p_k}$ be its activation value.
Firstly, we initiliazed the $p$th layer with $N_p$ filters,
for which we set the connection parameters
$\left<\alpha_{p_{k_1}},\alpha_{p_{k_2}},\cdots,\alpha_{p_{k_{N_p}}}\right>$
randomized as strictly different value.

\section{Competition Between Receptive Fields: Highlighting Local Features}
some text here...

\section{Overall Neural Network Model}
some text here...

\section{Image Compression based on Color Clustering}
Using basic pixel color filters
$$\left\{{\delta}_i(r,g,b)= \vec{w_i}\cdot(r,g,b)|i\in{[1,M]}\right\}$$
$M$ is the number of color filters for images.

\section{Train Filters Layer By Layer}
Object Detection Filters
$$\left\{\xi_i(\mathcal{F}_k) | i\in\left[1,N_k\right] \right\}$$
$\mathcal{F}_k$ is the $k$th receptive field on last CNN pooling layer.
$N_k$ is the number of filters for Object Detecton Filters, which refers to
layers from the second in CNNs.
\\
Due to huge computation duplicate, applying sampling methods:
Randomly select an image from database, and randomly select a field,
with coordinates as $(x,y)$ while keeping width and height as constant.
The width and height is determined by filters.
Use this piece as input to train fileters layer by layer unsupervisedly.

\section{Data-driven sparse Connections}
As showed in the previous chapter, we train filters layer by layer,
Generally, if we are now at $p\text{th}(p\ge2)$ layers, we have trained all
$q\text{th}(q<p)$ layers.\\
  Inspired by biological brain, we apply Lateral Depression model to the unsupervised
training.\\
Given a coefficient $\beta$ as minimum gap between activation of nodes.
If there exists one node $\mathcal{N}_{s_0}$ ($\mathcal{N}_{s_i}$ is the $i$th node
in $s$th layer), whose activation for current input is higher than its neighbors $\mathcal{U}_{s_0}$
(the neighbors, determined by some neighbor definition) nodes by at least $\beta$.
\begin{equation}
\mathcal{N}_{s_i} =\left\{
\begin{aligned}
1,&\quad \text{if }\sigma\left(\vec{w_{s_i}}\cdot\vec{x}\right) -
\sigma\left(\vec{w_{s_j}}\cdot\vec{x}\right) \ge \beta
(\text{for any }j\in \mathcal{U}_{s_i})  \\
0,&\quad \text{otherwise}\\
\end{aligned}
\right.
\end{equation}

>>>>

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Lateral Inhibition Nets with Nonlinear Connections}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Convolutional Neural Networks(CNNs) have achieved great success in
many computer vision tasks, especially in image recognition. However,
as neural networks grow deeper and deeper, to some extend, we've found
them becoming difficult to train, and requiring samples in large scale
dramatically, even with the help of Dropout and Dropconnect methods,
which do improve the accuracy a bit but burdens the training process as
a sacrifice. To overcome this, we proposed a novel method to generate
dynamic graphs of computation for varied inputs. As our computation
graphs are determined by input samples and proved to be pretty sparse,
we call them Data-driven Sparse Connections(DSCs). We've applied our DSCs
to a few popular image recognition tasks, and it is shown deep CNNs with
DSCs win over the state-of-the-art on many tasks, such as MNIST, FICAR-10,
and FICAR-100, to name a few.
\end{abstract}

@@

\section{Nonlinear Connections}
\subsection{Conventional Connections: Linear Computation Model}
In connection models known so far,
the most popular and probably the most useful one \cite{jain1996artificial} is :
$$ y=\sigma\left(\sum_{i=1}^{N}w_ix_i+b\right) $$
While, the activation function $\sigma(\cdot)$ can be the sigmoid function
$sigmoid(x)=\frac{1}{1+e^{-x}}$, or $tanh(x)$,
or ReLU function $ReLU(x)=\max(0,x)$\cite{nair2010rectified}.
In addition,
a different form of activation function, $maxout(x)=\max_{i=1}^N(w_ix_i)$,
is being used in CNNs recently\cite{goodfellow2013maxout}.
However, these activation functions are all neuron-based, and simply suppose
that each connection acts as simple as a linear function, $o(x_i)=w_ix_i$,
in which, $w_i$ is a float number without even a bound. While in biological
neural system, synapses, mimicked by artificial connections, are not really
behaving linearly.

\subsection{Nonlinear Computation Model for Connections}
Inspired by biological neuron synapses\cite{hall1905textbook,
bayliss1908reciprocal,gerard1941interaction}, we propose a new computation
model for connections between neurons.
In synapses, signals are transformed from electrical form
to chemical one, and transferred by some proteins to a connected neuron,
then again, transformed back to electrical form to inhibit or activate
the connected neuron\cite{gray1959axo,harvey2007locally}. In this process,
signals can be amplified or reduced, but not in a linear way. Futhermore,
signal strengths have lower and upper bounds which differs from the denotation
of connections in CNNs.

Suppose, there're 3 neurons, $\mathcal{N}_a$,$\mathcal{N}_b$,
$\mathcal{N}_c$, and 2 connections, $\mathcal{C}_{a\rightarrow c}$,
$\mathcal{C}_{b\rightarrow c}$, the graph is shown in figure
(\ref{fig:neurons}).

\begin{figure}
\centering
\includegraphics[height=24mm]{paper_res/conn.png}
\caption{A Net with Nonlinear Connections}
\label{fig:neurons}
\end{figure}

As synapses have two kinds: excitatory and inhibitory ones
\cite{uchizono1965characteristics,wilson1972excitatory},
we propose two categories of connections the same way.
For excitatory connections, as $\mathcal{C}_{a\rightarrow c}$
shown in figure (\ref{fig:neurons}), their signal
transferring functions are described as equation
(\ref{eq:excitatory-transfer}), in which, $\alpha\in(0,1)$
is guaranteed.
For excitatory connections,
\begin{equation}
    g^{+}(x)=\min\left(\max\left(0,\frac{x-\alpha}{1-\alpha}\right),1\right)
    \label{eq:excitatory-transfer}
\end{equation}

@@

For a $M$-layer neural network, The forward-computaton equation for the
$k^{\text{th}}$ neuron on $(p+1)^{\text{th}}(p=1,2,\cdots,M)$ layer,
$\mathcal{N}_{p_k}$, with the input layer denoted as the first layer, is

@@

In which, $g_{i\rightarrow{k}}$ is the signal transferring function from
$i^{\text{th}}$ neuron in $p^{\text{th}}$ layer to $k^{\text{th}}$ neuron
in $(p+1)^{\text{th}}$ layer,
and $o_{p_i}$ is the activation value of the $i^{\text{th}}$ neuron on
$p^{\text{th}}$ layer.

@@

\subsection{Error Backpropagation For Nonlinear Connections}
While, since the equations for connections and activation function
of neurons in our model are not really differentiable, the famous
backprop algorithm cannot be applied in the training section. Thus,
we propose a training algorithm that deals with non-differentiable
situation like this.

Firstly, let's introduce two model parameters: $\xi$ and $\eta$,
they together determine the learning rate of our model. In addition,
$\xi\in(0,1)$ and $\eta\in(0,1)$. Let
$x=\sum_{i=1}^{N_p}g_{i\rightarrow{k}}(o_{p_i})$, $y=\sigma(x)$, and the given
feedback error for current neuron $\mathcal{N}_{p_k}$ is $\Delta y$.
Similarly, the feedback error for $x$ is $\Delta x$. In case parameter $\alpha$
goes to 1 and fails our equations, we propose a upper-bound $\alpha_{\max}$, which
is very close to 1 but less than 1.
Thus, the parameter updatng rules are,

@@

\begin{equation}
\Delta{\alpha} =\xi\cdot\left\{
    \begin{aligned}
        &\left(\max\left(0,\hat{\alpha}\right)-\alpha\right),&\Delta{y}>0\\
        &\left(\min\left(\alpha_{\max}, \hat{\alpha}\right)-\alpha\right),&\Delta{y}<0\\
    \end{aligned}
    \right.
\label{eq:delta-alpha}
\end{equation}

@@

Let $\alpha_{p_{i\rightarrow{k}}}$ be the parameter of the connection from the
$i^{\text{th}}$ neuron in $p^{\text{th}}$ layer to the $k^{\text{th}}$ neuron in $(p+1)^{\text{th}}$ layer.
Using equation (\ref{eq:delta-alpha}), we can update the parameters of connections.
For excitatory connections,

@@

\begin{equation}
    \Delta\alpha_{p_{i\rightarrow{k}}} =\xi\cdot
    \left\{
        \begin{aligned}
            &\max\left(0,\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}>0\\
            &\min\left(\alpha_{\max},\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}<0\\
        \end{aligned}
        \right.
    \label{eq:conn-update-pos}
\end{equation}

@@

\begin{equation}
    \Delta\alpha_{p_{i\rightarrow{k}}} =\xi\cdot
    \left\{
        \begin{aligned}
            &\min\left(\alpha_{\max},\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}>0\\
            &\max\left(0,\hat{\alpha}_{p_{i\rightarrow{k}}}\right)-\alpha_{p_{i\rightarrow{k}}},\\
            &\quad\quad\Delta x_{p+1_{i\rightarrow{k}}}<0\\
        \end{aligned}
        \right.
    \label{eq:conn-update-neg}
\end{equation}

@@

We propose a valve $\tau\in(0,\alpha_{\max})$, which is very close to 0 but greater
than 0, if $g_{p_{i\rightarrow{k}}}=g^{+}$, $\Delta x_{p+1_{i\rightarrow{k}}}<0$
and $\alpha_{p_{i\rightarrow{k}}}+\Delta\alpha_{p_{i\rightarrow{k}}}-\alpha_{\max}<\tau$,
then for connection $\mathcal{C}_{p_{i\rightarrow{k}}}$, let $g_{p_{i\rightarrow{k}}}=g^{-}$, this update will
switch connections from excitatory to inhibitory.
Similarly, if $g_{p_{i\rightarrow{k}}}=g^{-}$, $\Delta x_{p+1_{i\rightarrow{k}}}>0$
and $\alpha_{p_{i\rightarrow{k}}}+\Delta\alpha_{p_{i\rightarrow{k}}}-\alpha_{\max}<\tau$,
then for connection $\mathcal{C}_{p_{i\rightarrow{k}}}$, let $g_{p_{i\rightarrow{k}}}=g^{+}$, this update will
switch connections from inhibitory to excitatory.

So far we've derivated the equations for updating parameters of neurons
in $(p+1)^{\text{th}}$ layer and the parameters of connections from $p^{\text{th}}$ layer to
$(p+1)^{\text{th}}$ layer. With equation (\ref{eq:delta-x-real}),(\ref{eq:conn-error})
and (\ref{eq:delta-x}), we calculate the error of the output in the $p^{\text{th}}$ layer.
Let $\Delta o_{p_{i\rightarrow{k}}}$ be the correction for $\mathcal{N}_{p_i}$
contributed by connection $\mathcal{C}_{p_{i\rightarrow{k}}}$,
for excitatory connections,

@@

\section{Lateral Inhibition Nets}
\subsection{The Theory of Lateral Inhibition}
Biologically, the excitation process of neurons are inhibited by nearby excited
neurons, so called \emph{Lateral Inhibition}
\cite{amari1977dynamics,blakemore1972lateral,blakemore1970lateral}.
Researches proved that the lateral inhibition play a big role in forming patterns
in neural dynamics\cite{amari1977dynamics}.
We propose an similar mechanism in artificial neural networks, and expect to
achieve better presentation of feature map.

Let $\dot{\Upsilon}$ be the set of all nearby neurons, i.e., the neighbors of a
neuron $\mathcal{N}_0$, and $\Upsilon = \dot{\Upsilon} \cup \{\mathcal{N}_0\}$.
For general argument, if the neuron $\mathcal{N}_0$ is at position $(x,y)$
in the $i^{\text{th}}$ feature map of $p^{\text{th}}$ layer in a convolutional
neural network. Let $r\in\mathbf{N}^{+}$ be the radius of neighborhood, the center
point is $(x_0,y_0)$, thus region defined by $(x_0,y_0)\odot{r}$ is the neighborhood, and every neuron
that is away from $\mathcal{N}_0$ by an Manhattan distance within $r$ is counted in $\Upsilon$.
that is, $\Upsilon=\{\mathcal{N}_{(x,y)}\mid|x-x_0|+|y-y_0|\le r\}$, then the
lateral inhibition phase is described with equation (\ref{eq:lateral-inhibition}).

\begin{equation}
    o'_{\mathcal{N}_0}=\frac{o_{\mathcal{N}_0}}{\max(1, \sum_{\mathcal{N}_i\in\Upsilon}o_{\mathcal{N}_i})}
    \label{eq:lateral-inhibition}
\end{equation}

In equation (\ref{eq:lateral-inhibition}), $o_{\mathcal{N}_0}$ is the activation
value of neuron $\mathcal{N}_0$, and $o'_{\mathcal{N}_0}$ is the real activation
value after the lateral inhibition phase.
As the forward computing flow is changed with this additional phase, the error
backprop equations need to be updated, as in equation (\ref{eq:lateral-inhibition-backprop}).

\begin{multline}
    \Delta{o_{\mathcal{N}_0}} = ({o'}_{\mathcal{N}_0}+\Delta{o'}_{\mathcal{N}_0})\cdot
        \max(1, \sum_{\mathcal{N}_i\in\Upsilon}o_{\mathcal{N}_i} + \Delta{o'}_{\mathcal{N}_0})\\
    -{o'}_{\mathcal{N}_0}\cdot\max(1,\sum_{\mathcal{N}_i\in\Upsilon}o_{\mathcal{N}_i})
    \label{eq:lateral-inhibition-backprop}
\end{multline}

\subsection{A Visualized Instance of Lateral Inhibition}
To visualize how lateral inhibition can improve the presentation of feature maps
from original images, we propose a simple filter which only extracts perceived
luminance distribution of an image, denoted as $\mathcal{F}(\cdot)=(0.299,0.587,0.114)\cdot(r,g,b)$.
Such a filter has a size of receptive field as $1\times1$. We conduct this experiment
under \emph{Jupyter Notebook} (thanks to all supporters of this amazing staff), and
the image to test (see Fig-\ref{fig:lateral-inhibition-test-original})
is randomly chosen from Web (no offence to the president of the U.S.).

\begin{figure*}[!t]
\centering
\subfloat[The Original]{\includegraphics[width=1.5in]{paper_res/trump.png}
\label{fig:lateral-inhibition-test-original}}
\hfil
\subfloat[Luminance Filter]{\includegraphics[width=1.5in]{paper_res/trump-filtered.png}
\label{fig:lateral-inhibition-test-filtered}}
\hfil
\subfloat[Lateral Inhibition]{\includegraphics[width=1.5in]{paper_res/trump-lateral-inhibition.png}
\label{fig:lateral-inhibition-test-lateral-inhibition}}
\hfil
\subfloat[Binarization]{\includegraphics[width=1.5in]{paper_res/trump-binarization.png}
\label{fig:lateral-inhibition-test-binarization}}
\caption{Lateral Inhibition Visualization}
\label{fig:lateral-inhibition-test}
\end{figure*}

Using the Luminance Filter $\mathcal{F}$, we get Fig-\ref{fig:lateral-inhibition-test-filtered},
which is generally considered as a grayscale image from the original.
In conventional neural nets, such a feature map generated by this filter is
connected directly to a sub-sampling or fully-connected layer, the connection volume
and computation cost thereby are considerable, and often lead to overfitting\cite{goodfellow2013maxout}.
To overcome this, we append lateral inhibition phase immediately to each of convolution layer
before the computation process enters into next layer, expecting to make a relatively more sparse net.
The result for current case is shown as Fig-\ref{fig:lateral-inhibition-test-lateral-inhibition}.
The darker part of image is what is expected to extract. As we see, the lateral inhibition
phase performs similarly to a differential calculus of images, but with more global features
(such as luminance) remained. Let's see how this works, suppose a part of single channel image
is denoted as a float matrix $\mathbf{M}$,

\begin{equation}
\mathbf{M} = \left\{
\begin{aligned}
    0.1\quad0.0\quad0.1\quad0.9\quad0.9\quad0.9\\
    0.0\quad\mathbf{0.4}\quad0.0\quad0.9\quad\mathbf{0.9}\quad0.9\\
    0.1\quad0.0\quad0.1\quad0.9\quad0.9\quad0.9\\
\end{aligned}
\right\}
\notag
\end{equation}

Notice that only the emphasized part of matrix $\mathbf{M}$ is under observation.
Let the lateral inhibition phase be $\Omega(r)$ in which $r$ is the only parameter
for the definition of neighborhood $\Upsilon$, according to equation (\ref{eq:lateral-inhibition}),

\begin{multline}
\mathbf{M'}=\mathbf{M}\otimes\Omega(r=1) = \\
\left\{
\begin{aligned}
    0.1\quad    0.0\quad            0.1\quad    0.32\quad    0.25\quad          0.33\\
    0.0\quad    \mathbf{0.4}\quad   0.0\quad    0.25\quad    \mathbf{0.2}\quad  0.33\\
    0.1\quad    0.0\quad            0.1\quad    0.32\quad    0.25\quad          0.33\\
\end{aligned}
\right\}
\notag
\end{multline}

Before lateral inhibition phase, the left half of $\mathbf{M}$ is a 'darker' place
(the smaller, the darker),
compared to its right one. While, after $\Omega(r=1)$ is applied, the left half
remained unchanged, and the right half of $\mathbf{M'}$ is obviously suppressed,
and the right observed identity becomes surprisingly far smaller than the left.
While, we can see that the left half of the matrix still remained 'darker' than the right half,
which means lateral inhibition can keep the global features from images, and
highlights local features at the same time.

\section{Binarization of Feature Map}
\subsection{Feature Map Visualization}
Although the feature map drawn by the luminance filter is clearly visualized and understood
in last section, filters can be arbitrary and ambiguous in neural networks like CNNs,
and it thereby becomes difficult or even impossible to understand what kind of features those
filters really extract from the images.
However, if the lateral inhibition phase is employed,
we may obtain a better understanding and visualization of the feature maps, since we do not need
to care what the feature map really means, but just to know what differences are presented
among local regions of feature maps, as those differences are what truly determine which class
the input image is related to.

On the other hand, conventional visualization of feature maps simply
colorize those feature activation matrix into pactchs of image, and an average man may not get any useful information
to understand how convolutional networks work, or if they are working in a way as expected.
Recently a category of deconvolutional network is proposed to visualize the feature maps, and it seems
working well\cite{zeiler2014visualizing}. However, the method is literally too
complicated and requires much more computation, which we may not expect.

Therefore, we propose \emph{feature map binarization} to help visualize and diagnose each feature layer of CNNs
at literally no cost (the visualization is straightly one snapshot of the layer without any more
procedure as you will see).

For any type of layer at depth $p$, consisting of $N_p$ filter(s)
(actually, we may view a fully connected layer as a convolutional layer with only
single filter of which the receptive field is maximumized as the same size of last layer),
we get $N_p$ feature map(s).
For each feature map, $\Phi_{p_i},i=1,2,3,\cdots,N_p$, let $o_{p_{i_j}}'$ be the
$j^{\text{th}}$ element in map $\Phi_{p_i}'$, which is a state of $\Phi_{p_i}$ following lateral inhibition phase,
and $\dot{\Upsilon}_{p_{i_j}}$ be its neighborhood (the definition of neighborhood
preserves the same as that in lateral inhibition phase, while the parameter $r$ may be set alone),
we apply such procedure to binarize feature map $\Phi_{p_{i_j}}'$,

\begin{equation}
    \Xi_{p_{i_j}} = \{{o_{p_{i_k}}'}\mid{o_{p_{i_j}}'}-{o_{p_{i_k}}'}>\beta,o_{p_{i_k}}'\in\dot{\Upsilon}_{p_{i_j}} \}
    \label{eq:binarization-1}
\end{equation}

\begin{equation}
o_{p_{i_j}}'' =\left\{
\begin{aligned}
    1.0,\quad& \frac{\text{count}(\Xi_{p_{i_j}})}{\text{count}(\dot{\Upsilon}_{p_{i_j}})}\ge\theta \\
    0.0,\quad& \text{otherwise}\\
\end{aligned}
\right.
\label{eq:binarization-2}
\end{equation}

In equation (\ref{eq:binarization-1})(\ref{eq:binarization-2}), $\beta\in[0,+\infty]$ is the minimum gap
of activation proposed between any element in neighborhood $\dot{\Upsilon}_{p_{i_j}}$ and the interested one $o_{p_{i_j}}$,
and $\theta\in[0,1]$ is the lowerbound of the ratio of satisfied neighbors by the filter of minimum gap of activation.
Such that the binarization of feature maps is determined and only, on parameters $\left<r,\beta,\theta\right>$.

According to equation (\ref{eq:binarization-1}) and (\ref{eq:binarization-2}), we append our binarization phase
into the whole computing flow following the lateral inhibition phase. Thus we get Fig-\ref{fig:lateral-inhibition-test-binarization}
as the binarization result of the feature map, for which we take $\left<r,\beta,\theta\right>=\left<5,0.0,0.85\right>$.
From Fig-\ref{fig:lateral-inhibition-test-binarization}, we can clearly see what the luminance filter really extracts
from the original image, and basically how well it behaves.

\subsection{Input Determined Sparsity}
In fact, we may present the computing flow for each filter as the transformations of its feature map,
$$\mathbf{X}\longmapsto\cdots\longmapsto\Phi_{p_i}\overset{\Omega(r)}{\longmapsto}\Phi_{p_i}'\overset{\Psi(r,\beta,\theta)}{\longmapsto}\Phi_{p_i}''$$,
with $\Psi$ defined as the binarization phase. We take $\Phi_{p_i}'$ as the final state of feature map generated by
filter $\mathcal{F}_{p_i}$, and $\Phi_{p_i}''$ is the mask of its sparsity.
Obviously, $\Phi_{p_i}''$ is determined by its input $\mathbf{X}$, which may be an original image.
For each different input of a net, the sparsity mask may vary, and this is different from the Dropout\cite{hinton2012improving}
and Dropconnect\cite{wan2013regularization} regularization, which randomly reduce nodes or connections to train submodels of a net.

\section{Filter Polarization}
In conventional CNNs, due to huge volume of connections and sometimes insufficient training
data (big data though, not big enough yet), the redundancy of filters leads to model
overfitting and difficulty in training\cite{jaderberg2014speeding,chen2015compressing}.
Thus we propose a method called filter polarization,
it generates and pretrains those filters layer by layer, dynamically
determines the number of filters for each layer, and produces more polarized filters,
aiming to reduce the filter redundancy of nets and speed up global training.

Filter polarization algorithm contains three phase, they are executed in distinct order,
and the whole flow of three phases will iterate itself till some condition meets.

\subsection{Filter Generation}

\subsection{Filter Pretraining}

\subsection{Filter Redundancy Check}

Let $\mathcal{F}_{p_k}$ denote the $k^{\text{th}}$ filter in layer of
depth $p$, and $o_{p_k}$ be its activation value.
Firstly, we initiliazed the $p^{\text{th}}$ layer with $N_p$ filters,
for which we set the connection parameters
$\left<\alpha_{p_{k_1}},\alpha_{p_{k_2}},\cdots,\alpha_{p_{k_{N_p}}}\right>$
randomized as strictly different values.

\section{Imperical Study}
We propose a net model to achieve automatic image recognition, and it is tested
on a set of popular benchmarks.

On MNIST datasets, with no convolutional layers, we've achieved accuracy and
minimum training cost.

------------- CHART HERE -------------

On CIFAR-10 benchmark, we use convolutional layers to reduce parameter volume
and enhence model robustness. Our model performs well too.

------------ CHART HERE --------------

For small sample volume datasets like CIFAR-100 benmark, our model also outperforms
most state-of-the-art ones.

------------ CHART HERE --------------
